DOpElib:\\ Differential Equations and Optimization Environment

### 2013-12-10 Examples/OPT/StatPDE/Example8/content.tex
Finished exchange of the examples

\subsubsection{General problem description}
This example implements the topology optimization of an MBB-Beam given in \\
{\tt OPT/StatPDE/Example6} using the SIMP method.

The solution is computed using the commercial optimization library SNOPT as in 
{\tt OPT/StatPDE/Example7}. This Example demonstrate how global constraints on
the control variable can be included into the optimization call.

>>>>

\subsubsection{General problem description}
This example implements the topology optimization of an MBB-Beam given in \\
{\tt OPT/StatPDE/Example7} using the SIMP method.

The solution is computed using the commercial optimization library SNOPT, similar 
to {\tt OPT/StatPDE/Example6} where IPOPT is used. 
This Example demonstrate how global constraints on
the control variable can be included into the optimization call.
